The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-30 Writeup/paper_v3.tex
higher z - CANDELS
Tim comment on areas

It is important to keep in mind the nature of COSMOS with respect to
other possible {\em HST} training samples.  COSMOS represents the
largest contiguous field surveyed by the {\em HST}, with the sizes of
other {\em HST} fields such as GOODS and AEGIS lagging by at least an
order of magnitude.  Hence, if cosmic variance due to structures along
the line-of-sight in COSMOS are problematic for its use as a training
sample for weak lensing simulations, studies that use even smaller
area training samples are even more prone to errors, with the UDF
serving as an extreme case.  If the size of the {\em HST} survey is
small enough, there is no reason {\em a priori} to suppose that the
galaxy population is typical even when using all galaxies along the
line of sight, without any division into redshift bins.  Of course,
future surveys are unlikely to pick just a single survey to serve as
the basis for their image simulation training sample, but rather
will combine as many as possible.  Combining multiple surveys will
reduce the cosmic variance and therefore the significance of the
effects discussed in this work.
However, as COSMOS is significantly larger than other \emph{HST} surveys, combining COSMOS with smaller fields is unlikely to ameliorate this effect.
Thus, it will be important to carefully choose the size of redshift slices used to
derive properties of the galaxy population so as to be minimally
affected by this issue.

A final consideration is the question of how applicable these results
using volume-limited samples are to simulations of upcoming weak
lensing surveys, which will exclusively use flux-limited samples.  For
our analysis, the volume-limiting sample was necessary to avoid
complications due to varying galaxy populations in each redshift
slice, allowing us to isolate purely environmental effects.  In
principle, if the morphology-density correlations that we have
identified turn out to not exist for intrinsically fainter galaxy
populations, then at low redshift (where a flux limited sample will
include galaxies that are intrinsically much fainter than at high
redshift), the effects will be less serious for upcoming lensing
surveys.  However, we do not have any particular reason to believe
that these effects will vanish for fainter galaxies.  Moreover, at
higher redshift where only intrinsically bright galaxies can be seen,
the effect should be present at a level similar to what we have found
here.  Since higher redshift galaxies tend to dominate cosmological
shear estimates (due to their higher shears), our findings will be
important to take into account.

>>>>

It is important to keep in mind the nature of COSMOS with respect to
other possible {\em HST} training samples.  COSMOS represents the
largest contiguous field surveyed by the {\em HST}, with the sizes of
other {\em HST} fields such as GOODS and AEGIS lagging by at least a
\rachel{factor of 6 (for GEMS, more for AEGIS and GOODS)}.  Hence, if cosmic variance due to structures along
the line-of-sight in COSMOS are problematic for its use as a training
sample for weak lensing simulations, studies that use even smaller
area training samples are even more prone to errors, with the UDF
serving as an extreme case.  If the size of the {\em HST} survey is
small enough, there is no reason {\em a priori} to suppose that the
galaxy population is typical even when using all galaxies along the
line of sight, without any division into redshift bins.  Of course,
future surveys are unlikely to pick just a single survey to serve as
the basis for their image simulation training sample, but rather
will combine as many as possible.  Combining multiple surveys will
reduce the cosmic variance and therefore the significance of the
effects discussed in this work.
However, as COSMOS is significantly larger than other \emph{HST} surveys, combining COSMOS with smaller fields is unlikely to ameliorate this effect.
Thus, it will be important to carefully choose the size of redshift slices used to
derive properties of the galaxy population so as to be minimally
affected by this issue.

A final consideration is the question of how applicable these results
using volume-limited samples are to simulations of upcoming weak
lensing surveys, which will exclusively use flux-limited samples.  For
our analysis, the volume-limiting sample was necessary to avoid
complications due to varying galaxy populations in each redshift
slice, allowing us to isolate purely environmental effects.  In
principle, if the morphology-density correlations that we have
identified turn out to not exist for intrinsically fainter galaxy
populations, then at low redshift (where a flux limited sample will
include galaxies that are intrinsically much fainter than at high
redshift), the effects will be less serious for upcoming lensing
surveys.  However, we do not have any particular reason to believe
that these effects will vanish for fainter galaxies.  Moreover, at
higher redshift where only intrinsically bright galaxies can be seen,
the effect should be present at a level similar to what we have found
here.  Since higher redshift galaxies tend to dominate cosmological
shear estimates (due to their higher shears), our findings will be
important to take into account.  \rachel{It would also be advisable to
  carry out a future study of this effect at higher redshift (beyond
  $0.85$), using for example the data from the CANDELS survey.}
